Concurrent Programming in Harmony

### 2021-10-31 book/paper.tex
Latest
Added "where" clause to select statement
Introducing "countLabel", which counts the number of threads at a label

Operations on program counters include the following:
\begin{center}
\begin{tabular}{|l|l|}
\hline
\texttt{$m$ $a$} & invoke method with program counter $m$ and argument $a$\\
\hline
\texttt{atLabel $l$} & return a bag of (method, argument) pairs of threads executing at label $l$ \\
\hline
\end{tabular}
\end{center}

@@

\subsection*{\textbf{for ... in [...where]}}

@@

The statement \textbf{possibly $b_1, b_2, ...$} atomically evaluates all
predicates $b_i$.
At completion, Harmony reports which of the predicates never held.

\subsection*{\textbf{select ... in}}

@@

>>>>

Operations on program counters include the following:
\begin{center}
\begin{tabular}{|l|l|}
\hline
\texttt{$m$ $a$} & invoke method with program counter $m$ and argument $a$\\
\hline
\texttt{atLabel $l$} & return a bag of (method, argument) pairs of threads executing at label $l$ \\
\texttt{countLabel $l$} & return the number of threads executing at label $l$ \\
\hline
\end{tabular}
\end{center}

@@

\subsection*{\textbf{for ... in ... [where ...]}}

@@

The statement \textbf{possibly $b_1, b_2, ...$} atomically evaluates all
predicates $b_i$.
At completion, Harmony reports which of the predicates never held.
While \texttt{assert} statements check that nothing ever goes wrong,
\texttt{possibly} statements can check that certain things sometimes
go right.

\subsection*{\textbf{select ... in ... [ where ... ]}}

@@

The optional \textbf{where} clause can be used to filter the set down to the elements
that satisfy the condition following the \textbf{where} keyword.
